\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-06-01 AffineLieAlgebras/InformalNotes/article.tex

Let's describe the reduction of the fundamental representation of $B_2$ with the highest weight equal to $(1,0)$ (in the fundamental weight basis), it is drawn as the black vector in the Figure \ref{fig:B2_A1}.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
There we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of the fundamental representation of $B_2$ with the corresponding determinants $\epsilon(\omega)$ of Weyl transformations.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the regular embedding $B_2 \longrightarrow B_4$.
We calculate the branching coefficients for the fundamental vector representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
  \label{fig:dynkin}
\end{figure}

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
\begin{figure}[h!tb]
  \centering
    \includegraphics[width=100mm]{B4_B2_anom_points.pdf}
  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[h!tb]
  \centering
  \includegraphics[width=80mm]{B4_B2_fan.pdf}
  \caption{The fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{multline}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{multline}

>>>>

Let's describe the reduction of the fundamental representation of $B_2$ with the highest weight equal to $(1,0)$ (in the fundamental weight basis), it is drawn as the black vector in the Figure \ref{fig:B2_A1}.
\begin{figure}[th]
  \noindent\centering{
    \includegraphics[width=80mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
There we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of the fundamental representation of $B_2$ with the corresponding determinants $\epsilon(\omega)$ of Weyl transformations.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[t]
  \noindent\centering{
    \includegraphics[width=80mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules for the embedding $A_1\subset B_2$}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the regular embedding $B_2 \longrightarrow B_4$.
We calculate the branching coefficients for the fundamental vector representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[h]
  \centering
  \includegraphics[width=50mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
  \label{fig:dynkin}
\end{figure}

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
\begin{figure}[p]
  \centering
    \includegraphics[width=90mm,height=90mm]{B4_B2_anom_points.pdf}
  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=80mm,height=80mm]{B4_B2_fan.pdf}
  \caption{The fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{multline}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{multline}

### 2010-06-01 AffineLieAlgebras/InformalNotes/talk.tex

Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований. В $D$-мерном случае генераторы у таких преобразований следующие:
\begin{align}
  \label{eq:1}
  & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
  &P_\mu \equiv-i\partial_\mu \,, \\
  &D \equiv-ix_\mu\partial^\mu \,, \\
  &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
\end{align}
На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
В двумерном случае существует бесконечное число локально-конформных преобразований.
Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций.

@@

Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсуммы на торе
(\ref{eq:2}) может быть записана в виде
\begin{equation}
  \label{eq:4}
    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
\end{equation}
где $\chi_j$ --- характер представления $\mathcal{H}_j$,
\begin{equation}
  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
\tau}
\end{equation}
Характеры переходят друг в друга при модулярных преобразованиях:
\begin{equation}
  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
\end{equation}
где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий
поля.

>>>>

Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.

%% В $D$-мерном случае генераторы у таких преобразований следующие:
%% \begin{align}
%%   \label{eq:1}
%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
%%   &P_\mu \equiv-i\partial_\mu \,, \\
%%   &D \equiv-ix_\mu\partial^\mu \,, \\
%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
%% \end{align}
%% 
На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
В двумерном случае существует бесконечное число локально-конформных преобразований.
Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar z)=0$).

@@

Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсуммы на торе
(\ref{eq:2}) может быть записана в виде
\begin{equation}
  \label{eq:9}
    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
\end{equation}
где $\chi_j$ --- характер представления $\mathcal{H}_j$,
\begin{equation}
  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
\tau}
\end{equation}
Характеры переходят друг в друга при модулярных преобразованиях:
\begin{equation}
  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
\end{equation}
где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий
поля.
